\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-13 bare_conf.tex
small fixes.

\begin{abstract}
%\boldmath
In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision. Combining standard smartphone device, external deep learning based vision processor and audio-tactile user interface into compact visual perception compensation device the suggested architecture may be advantageous both for researchers and industrial product developers.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

% External vision processor
%visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
Although modern high-end smartphones are quite powerful computers themselves, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g. server with graphics processing unit (GPU)). This motivates us to employ an external server for vision data processing. In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor} among others. After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.

@@

In this article we outlined an idea of complex computer vision-based  sensor architecture, which may help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface. Comparing to an existing commercial products e.g. \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset. Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G. Combined audio/tactile interface also may be more convenient for the users, since it allows to provide the feedback more efficiently, comparing to purely audio or purely tactile means.

>>>>

\begin{abstract}
%\boldmath
In this short article we describe and discuss high level architecture of computer vision-based system for partial compensation of lost or impaired human vision. Combining standard smartphone device, external deep learning based vision processor and audio-tactile user interface into compact visual perception compensation device the suggested architecture may be advantageous both for adacemic researchers and commercial product developers.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

% External vision processor
%visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
Although modern high-end smartphones are quite powerful computers themselves, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g. server with graphics processing unit (GPU)). This motivates us to employ an external server for vision data processing. In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, obstacle detection \cite{Laina}, action recognition \cite{Valor}, among others. After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.

@@

In this article we outlined an idea of complex computer vision-based  sensor architecture, which may help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface. Comparing to an existing commercial products e.g. \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset. Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of the mobile networks to 5G. Combined audio/tactile interface also may be more convenient for the users, since it allows to provide the feedback more efficiently, comparing to purely audio or purely tactile means.
